{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion}

### 2017-01-06 proposal/thesprop.tex
minor fixes
several small changes
NOOOOOOOOOOO

@@

\keywords{landslide terminal, baggage claim, ground transportation, ticketing}

@@

\begin{itemize}
	\item TODO % TODO
\end{itemize}

% TODO - make a timeline

>>>>

\newtheorem{theorem}{Theorem}

\newcommand\llama[1]{\includegraphics[width=#1]{llama.pdf}}
\newcommand\llitem{\item[\llama{1.2em}]}

@@

% TODO(thesis): Save this one for the thesis itself...
%\keywords{landslide terminal, baggage claim, ground transportation, ticketing}

@@

\begin{itemize}
	\item 2017 January: Submit thesis proposal, submit revised IRB proposal for planned user studies.
	\item 2017 ???uary: Present thesis proposal (whenever the committee is free).
	\item 2017 February-March: Develop ``grading'' TA user study and deploy it in 15-410 (Section~\ref{sec:grading}).
	\item 2017 March-August: Port Landslide to Bochs for use in Pintos OS classes (Section~\ref{sec:pintos-todo}).
	\item 2017 March-August: Implement, evaluate, and write paper about transactional memory project (Section~\ref{sec:tm}).
	\item 2017 August-October: Polish and deploy Pintos user study (Section~\ref{sec:pintos-todo}).
	\item 2017 ???ember: Resubmit paper about 410 user studies (Section~\ref{sec:studence}) (previously rejected from SIGCSE) (whenever an appropriate conference deadline arises.
	\item 2017 October-November: Deploy 410 TA grading study again for more data.
	\item 2017 December: Begin writing thesis.
	\item 2018 January-April: Write thesis. Also fill in miscellaneous gaps, such as the ``variance'' Quicksand experiments (Section~\ref{chap:quicksand}) and measuring Landslide's heuristics' accuracy (Section~\ref{sec:studence}).
	\item 2018 February-March: Deploy Pintos student and 410 TA studies one final time.
	\item 2018 April-May: Defend \& graduate.
\end{itemize}

%For pretty much any reason (much like hardware transactions),
%I may need to delay the timeline by a semester, defending instead in 2018 June.
%For example, the above plan to deploy a Pintos user study within one semester's time of finishing the open-source Landslide port is quite ambitious,
%assuming among other things smooth negotiations with the OS course staff at another university.
%Anyway, this is my optimistic proposal. Thanks for reading.
